%\documentclass[toc]{Template/PoS}
\documentclass{Template/PoS}

\usepackage{enumitem}
\usepackage{soul}
\setlist{nolistsep}

\title{Integrating Network-Awareness and Network-Management into PhEDEx}

\ShortTitle{Network-Management in PhEDEx}

\author{\speaker{Vlad L\v{a}p\v{a}d\v{a}tescu}\\
Caltech / USA\\
E-mail: \email{vlad@cern.ch}}

\author{Tony Wildish\\
Princeton / USA\\
E-mail: \email{awildish@princeton.edu}}

\author{ANSE Collaboration 
	\thanks{B. Ball, A. Barczyk, J. Batista, K. De, S. McKee, A. Melo, H. Newman, A. Petrosyan, P. Sheldon, R. Voicu}}

\abstract{
ANSE (Advanced Network Services for Experiments) is an NSF funded project, which aims
 to incorporate advanced network-aware tools in the mainstream production workflows of 
 LHC's two largest experiments: ATLAS and CMS. For CMS, this translates in the integration 
 of bandwidth provisioning capabilities in PhEDEx, its data-transfer management tool.

PhEDEx controls the large-scale data-flows on the WAN across the experiment, typically
 handling 1 PB of data per week, spread over 70 sites. This is only set to increase 
 once LHC resumes operations in 2015.

The goal of ANSE is to improve the overall working efficiency of the experiments, by 
allowing for more deterministic times to completion for a designated set of data transfers,
 through the use of end-to-end dynamic virtual circuits with guaranteed bandwidth.

Through our work in ANSE, we have enhanced PhEDEx, allowing it to control a circuit's 
lifecycle based on its own needs. By checking its current workload and past transfer 
history on normal links, PhEDEx is now able to make smart use of dynamic circuits, 
only creating one when it's worth doing so. Different circuit management infrastructures
 can be used, via a plug-in system, making it highly adaptable.

In this paper, we present the progress made by ANSE with regards to PhEDEx. We show how
 our system has evolved since the prototype phase we presented last year, and how it is
 now able to make use of dynamic circuits as a production-quality service. We describe 
 its updated software architecture and how this mechanism can be refactored and used 
 as a stand-alone system in other software domains (like ATLAS' PanDA). 

We conclude, by describing the remaining work to be done ANSE (for PhEDEx) and discuss 
on future directions for continued development.
}

\FullConference{International Symposium on Grids and Clouds (ISGC) 2015,\\
		15-20 March 2015\\
		Academia Sinica, Taipei, Taiwan}

\parindent=0pt 

\begin{document}
    
\input{section-1-Introduction.tex}
\input{section-2-Previous-results.tex}
\input{section-3-Updates.tex}
\input{section-4-Solution.tex}
\input{section-5-Conclusion.tex}
\input{section-6-Bibliography.tex}

\end{document}